\chapterwithopening{Literature Review and Theoretical Framework}{chap:literature_review}{
  \chaptercontentsitem{sec:literature_review_introduction}
  \chaptercontentsitem{sec:evolution_of_digital_education_platforms}
  \chaptercontentsitem{sec:research_gap_integrated_ecosystem}
  \chaptercontentsitem{sec:artificial_intelligence_in_education}
  \chaptercontentsitem{sec:benchmarking_fragmented_vs_integrated}
  \chaptercontentsitem{sec:theoretical_technical_foundations_eduverse}
}

\section{Introduction}\label{sec:literature_review_introduction}

This chapter presents the theoretical background for Eduverse. It reviews the
evolution of digital learning systems, the limitations of fragmented
educational tools, selected concepts from artificial intelligence in
education, and the main foundations that inform the system's design. The
discussion draws selectively from the literature on Learning Management
Systems, Artificial Intelligence in Education, Role-Based Access Control, and
educational platform architecture.

\section{Evolution of Digital Education Platforms}\label{sec:evolution_of_digital_education_platforms}

\subsection{From Traditional Classroom Management to Digital Learning Systems}\label{subsec:traditional_to_digital_learning_systems}

Educational management has historically depended on face-to-face coordination,
manual attendance records, printed materials, and locally maintained
assessment processes. As educational institutions expanded in scale and digital
communication became more common, Learning Management Systems emerged to
centralize course materials, announcements, assignment handling, and academic
tracking within a unified digital environment \cite{coates2005critical,dagger2007service}.

The move toward digital learning systems did not simply replace paper-based
administration with electronic storage. It introduced new expectations about
continuous access, asynchronous participation, online communication, and
traceable academic workflows. Modern educational platforms are therefore judged
not only by their capacity to store materials, but also by their ability to
support coordination, interaction, assessment, and institutional oversight
across different users and contexts \cite{selwyn2011education}.

\subsection{Limitations of Fragmented Learning Management Tools}\label{subsec:limitations_of_fragmented_learning_management_tools}

Although digital tools have become common in education, many institutions still
depend on separate services for class management, communication, file sharing,
video sessions, assessment, and student support. This fragmented model creates
operational discontinuity because activities that belong to the same academic
process are distributed across unrelated systems. As a result, students must
move repeatedly between platforms, while teachers and administrators face a
reduced ability to maintain clear academic oversight \cite{selwyn2011education,dagger2007service}.

When communication, submissions, live sessions, and evaluation records are
distributed across multiple tools, consistency, accountability, and access
governance become harder to maintain. The limitation is therefore
organizational as well as technical, because it weakens the integrity of the
educational environment itself.

\section{Research Gap and Proposed Integrated Learning Ecosystem}\label{sec:research_gap_integrated_ecosystem}

A clear gap exists between the broad range of activities required in modern
education and the way those activities are often supported by disconnected
systems. Institutions may rely on one tool for class coordination, another for
messaging, another for live teaching, another for assignments, and still
others for assessment, AI support, or programming practice. While each tool may
be effective in isolation, the overall experience remains fragmented and
operationally inefficient.

Eduverse addresses this gap by proposing an integrated learning ecosystem
rather than a collection of separate utilities. It brings class management,
communication, materials, assessment, live sessions, AI-assisted support, and
programming practice into one organizationally governed environment. The main
implemented client is the web application, while the mobile client remains an
MVP companion for selected daily-use workflows. This balance between
integration and controlled scope is central to the academic identity of the
project.

\section{Artificial Intelligence in Education}\label{sec:artificial_intelligence_in_education}

Artificial intelligence in education is commonly discussed as a means of
augmenting teaching and learning rather than replacing teachers or institutional
judgment \cite{luckin2016intelligence,holmes2019ai}. In educational settings,
AI systems are valuable when they improve access to explanations, support
learning continuity, reduce routine workload, and provide structured assistance
without undermining academic responsibility. In Eduverse, this perspective
frames the AI Agent as a bounded academic support service embedded in the
platform rather than as an authority over teaching or evaluation.

\subsection{Context-Aware Learning Assistance}\label{subsec:context_aware_learning_assistance}

One of the most important ideas in AI-supported education is that assistance is
more useful when it is tied to the learner's actual academic context. Generic
responses are often less effective than support that takes into account course
materials, class discussion, ongoing tasks, and instructional expectations.
Context-aware assistance can therefore improve relevance, reduce confusion, and
support more focused academic interaction \cite{holmes2019ai}.

In Eduverse, this means the AI Agent operates within the active class, user
role, and immediate learning task so that support remains relevant to the
current course activity. Its role is to assist understanding and clarification
rather than to substitute for teaching.

\subsection{Material Summarization and Learning Support}\label{subsec:material_summarization_and_learning_support}

Material summarization represents a practical form of AI assistance in
education. Long documents, learning materials, and instructional resources can
be difficult for students to process efficiently, especially when they are
working under time constraints or trying to review several academic topics in
parallel. AI-assisted summarization can support comprehension by highlighting
main points, reducing information overload, and helping learners return more
quickly to the central ideas of a topic \cite{luckin2016intelligence}.

This kind of support is most appropriate when it complements reading rather
than replacing it. In Eduverse, it is most relevant to class materials,
assignment instructions, and related course resources, where the AI Agent may
summarize or clarify content while keeping the original material central.

\subsection{Assessment and Feedback Support}\label{subsec:assessment_and_feedback_support}

AI can also support assessment-related workflows by assisting with draft
guidance, formative feedback, and structured academic support around tasks and
examinations. In theory, such support can help learners prepare, reflect on
their work, and identify areas that require improvement \cite{holmes2019ai}.
However, educational literature also emphasizes that AI use in assessment must
be governed carefully so that it supports learning without weakening academic
integrity or teacher responsibility \cite{luckin2016intelligence,holmes2019ai}.

For Eduverse, this means the AI Agent may assist students and teachers with
preparatory guidance, clarification, and formative support around assignments
and examinations, while final instructional judgment and assessment
responsibility remain with the teacher.

\section{Benchmarking: Fragmented Tools vs. Integrated Eduverse Approach}\label{sec:benchmarking_fragmented_vs_integrated}

Table~\ref{tab:fragmented_vs_integrated_eduverse} summarizes the difference
between a fragmented educational-tool model and the integrated approach
proposed by Eduverse.

\begin{table}[htbp]
\centering
\begingroup
\small
\setlength{\tabcolsep}{5pt}
\renewcommand{\arraystretch}{1.18}
\caption{Fragmented Educational Tools vs. Integrated Eduverse Approach}
\label{tab:fragmented_vs_integrated_eduverse}
\vspace{0.55em}
\begin{tabular}{|p{0.16\textwidth}|p{0.30\textwidth}|p{0.30\textwidth}|}
\hline
\rowcolor{gray!15}
{\raggedright\textbf{Educational Need}} &
{\raggedright\textbf{Fragmented Tool Approach}} &
{\raggedright\textbf{Integrated Eduverse Approach}} \\
\hline
{\raggedright Class management} &
{\raggedright Class records, memberships, and academic coordination are handled through separate administrative tools or partially manual processes.} &
{\raggedright Class organization is managed within one platform through organization-aware and role-based structures.} \\
\hline
{\raggedright Communication} &
{\raggedright Messaging and announcements are distributed across external chat or notification tools.} &
{\raggedright Communication remains connected to the academic environment and class context.} \\
\hline
{\raggedright Live sessions} &
{\raggedright Synchronous teaching depends on external meeting services disconnected from course workflows.} &
{\raggedright Live sessions are treated as part of the broader educational platform and linked to class participation.} \\
\hline
{\raggedright Materials and assignments} &
{\raggedright Learning resources and tasks are often stored, shared, and submitted through different services.} &
{\raggedright Materials and assignments are coordinated within the same academic workspace.} \\
\hline
{\raggedright AI support} &
{\raggedright AI tools are usually external and not directly tied to the learner's course context.} &
{\raggedright AI support is positioned within the class environment as contextual academic assistance.} \\
\hline
{\raggedright Programming practice} &
{\raggedright Coding activities, when needed, often require separate platforms or disconnected lab tools.} &
{\raggedright Programming practice can be supported through an integrated educational IDE within the platform ecosystem.} \\
\hline
{\raggedright Assessment} &
{\raggedright Examinations and grading may rely on detached tools with limited continuity or oversight.} &
{\raggedright Assessment workflows are integrated into the same role-aware educational system.} \\
\hline
\end{tabular}
\endgroup
\end{table}

\section{Theoretical and Technical Foundations of Eduverse}\label{sec:theoretical_technical_foundations_eduverse}

\subsection{Web-Based Educational Platforms}\label{subsec:web_based_educational_platforms}

Web-based educational platforms remain the strongest medium for full academic
management because they support richer interfaces, broader administrative
workflows, and deeper integration across organizational functions. They are
especially suitable for tasks such as class configuration, materials
management, assessment setup, and detailed instructional coordination.

From a theoretical standpoint, web environments are architecturally well suited
to full academic management because they can centralize complex interfaces,
persistent records, administrative controls, and cross-workflow coordination
within one accessible system.

\subsection{Mobile Companion Learning Applications}\label{subsec:mobile_companion_learning_applications}

Mobile educational applications play a different but still important role in
digital learning environments. Their strength lies in quick access, timely
participation, and support for routine high-frequency actions such as checking
notifications, reviewing assignments, opening materials, and joining live
sessions. As a result, they are especially useful as companion systems for
daily academic engagement.

In Eduverse, the mobile client should therefore be understood as an MVP
companion rather than as a complete replacement for the main platform. It
extends accessibility to core user-facing workflows while more comprehensive
management and authoring remain centered in the web application.

% TODO: Add scholarly citation(s) specifically addressing mobile companion
% applications in digital learning environments.

\subsection{Real-Time Virtual Classrooms}\label{subsec:real_time_virtual_classrooms}

Synchronous learning environments are an important part of modern educational
theory because they strengthen immediacy, interaction, and instructional
presence. When live classrooms are integrated into the broader academic
platform rather than isolated in external services, continuity between teaching,
communication, and follow-up becomes easier to maintain \cite{garrison2000critical}.

This foundation is relevant to Eduverse because live sessions are not treated
as a separate product layer. Instead, they are part of the integrated learning
environment and serve the broader goal of linking synchronous participation
with the rest of the class workflow.

\subsection{Integrated Coding Environments for Programming Education}\label{subsec:integrated_coding_environments_programming_education}

Programming education often requires an environment in which learners can write
code, inspect results, practice problem solving, and remain connected to the
instructional context of the class. When coding practice is separated entirely
from the educational platform, students may lose continuity between learning
materials, teacher guidance, assignments, and practical execution.

An integrated coding environment addresses this problem by placing programming
practice within the same educational ecosystem as the rest of the academic
workflow. For Eduverse, the integrated IDE is therefore part of the platform's
broader pedagogical direction, especially for programming-related classes and
technical learning settings.

% TODO: Add scholarly citation(s) on integrated coding environments or browser-
% based programming practice in education.

\subsection{Security, Roles, and Data Management}\label{subsec:security_roles_and_data_management}

Trustworthy educational platforms depend on controlled access, clear role
distinctions, and dependable data management. Role-Based Access Control is
especially relevant in this context because it supports structured separation
between administrative, teaching, and learner permissions
\cite{sandhu1996rbac,ferraiolo2003rbac}. In educational systems, such
distinctions are necessary not only for security, but also for accountability
and appropriate institutional governance.

Data management is equally foundational. Educational systems must maintain
reliable records, protect assessment-related information, and support different
types of content ranging from structured academic data to larger learning
materials and live-session interaction. From a theoretical perspective, this
requires a design orientation that treats security, data organization, and
permissions as core educational infrastructure rather than as secondary
technical concerns. This view is consistent with Eduverse, where access
control, data separation, and institutional structure are part of the
platform's trust model.

% TODO: Add additional citation(s) specifically supporting educational data
% governance and storage separation in learning platforms.

Taken together, these theoretical threads show that effective educational
platforms must reduce fragmentation while coordinating complementary forms of
support across web, mobile, synchronous, and practice-oriented learning
contexts. They also indicate that AI assistance, real-time instruction,
integrated coding environments, and secure data management are most valuable
when they operate within one coherent academic system rather than as detached
services. For Eduverse, this combined perspective provides the conceptual
basis for a unified platform model with differentiated client roles, bounded
AI support, live-session continuity, and protected institutional workflows.
The following chapters build on this foundation to explain the analysis,
design, and implementation choices of the project.
