\chapterwithopening{Methodology}{chap:methodology}{
  \chaptercontentsitem{sec:methodology_introduction}
  \chaptercontentsitem{sec:adopted_development_methodology}
  \chaptercontentsitem{sec:justification_for_methodology}
  \chaptercontentsitem{sec:development_phases}
  \chaptercontentsitem{sec:tools_and_technologies_used}
  \chaptercontentsitem{sec:team_workflow_and_project_management}
  \chaptercontentsitem{sec:methodological_challenges}
  \chaptercontentsitem{sec:methodology_summary}
}

\section{Introduction}\label{sec:methodology_introduction}

This chapter explains the methodology adopted for planning, analyzing,
developing, and refining Eduverse as a graduation project. The emphasis is on
the development process through which the project scope was transformed into a
working educational platform, rather than on the detailed technical
implementation of individual modules. The chapter therefore documents how the
project moved from problem understanding and scope definition to system
planning, feature development, service integration, and iterative refinement.

\section{Adopted Development Methodology}\label{sec:adopted_development_methodology}

Eduverse was developed using an iterative and incremental software development
methodology. This approach was appropriate because the project combines several
interdependent educational workflows, including organization management, class
coordination, materials, assignments, examinations, notifications, live
sessions, AI-assisted support, and programming practice. Rather than treating
the system as a single linear implementation task, development progressed
through repeated cycles of analysis, design, implementation, review, and
adjustment.

The methodology was also feature-oriented. Core workflows were prioritized
first, then expanded through successive refinements as the project structure
became more stable. Within this process, the web application served as the
main execution environment for the full platform, while the mobile application
was developed as an MVP companion focused on selected high-frequency academic
activities. This distinction supported scope control while preserving
functional coherence between the two clients.

\section{Justification for the Methodology}\label{sec:justification_for_methodology}

An iterative methodology was selected because Eduverse addresses a problem
domain that is broad in function but sensitive to scope. The platform had to
support multiple user roles, multiple organizations, synchronous and
asynchronous learning activities, and several specialized services without
turning the project into an unrealistic or weakly integrated system. A rigid
linear process would have made it more difficult to validate assumptions about
role behavior, workflow priorities, and the practical boundaries between the
web platform and the mobile companion.

The chosen methodology also matched the academic nature of the project.
Graduation projects typically benefit from gradual refinement because analysis,
design, implementation, and documentation evolve together rather than as
strictly isolated stages. For Eduverse, iterative development made it possible
to stabilize the class-centered platform model early, then extend it carefully
through live sessions, AI support, and the educational IDE while keeping the
mobile scope controlled and realistic.

\section{Development Phases}\label{sec:development_phases}

Although the project followed an iterative path, its progress can still be
understood through a set of major development phases. These phases provide a
structured view of how the project moved from conceptual problem analysis to a
working integrated platform.

\begin{table}[htbp]
  \centering
  \small
  \renewcommand{\arraystretch}{1.15}
  \setlength{\tabcolsep}{5pt}
  \caption{Eduverse Development Phases}
  \label{tab:eduverse_development_phases}
  \begin{tabular}{|>{\raggedright\arraybackslash}p{0.20\textwidth}|>{\raggedright\arraybackslash}p{0.41\textwidth}|>{\raggedright\arraybackslash}p{0.23\textwidth}|}
    \hline
    \textbf{Phase} & \textbf{Main Activities} & \textbf{Output} \\
    \hline
    Domain analysis & Studying fragmented educational workflows, user roles, and institutional needs & Initial problem model and platform direction \\
    \hline
    Scope definition & Identifying core features, priority users, and mobile MVP boundaries & Controlled project scope and feature priorities \\
    \hline
    Architecture planning & Organizing the system structure, data strategy, and external service roles & High-level architectural model \\
    \hline
    Web development & Building the primary academic workflows in the main client & Implemented web platform modules \\
    \hline
    Mobile development & Extending selected student and teacher workflows to the companion app & MVP mobile companion application \\
    \hline
    Integration and refinement & Connecting services, validating workflows, and correcting issues iteratively & More stable and coherent system behavior \\
    \hline
  \end{tabular}
\end{table}

\subsection{Problem Understanding and Domain Analysis}\label{subsec:problem_understanding_and_domain_analysis}

The first phase focused on understanding the educational problem that Eduverse
was intended to address. This included examining how materials, communication,
assignments, live teaching, examinations, and academic follow-up are often
distributed across separate tools. The analysis showed that fragmentation is
not merely inconvenient; it weakens continuity, increases administrative
overhead, and makes it harder for institutions to maintain a consistent view
of academic activity.

This phase also clarified the domain structure of the platform. The class was
identified as the central academic workspace, while the surrounding
organizational context established the need for role-aware access and
multi-organization support. The major user roles examined in this phase were
organization owner, organization admin, teacher, and student, since these
roles define both platform permissions and workflow expectations.

\subsection{Requirement Collection and Scope Definition}\label{subsec:requirement_collection_and_scope_definition}

After the problem domain was clarified, the next phase focused on translating
that understanding into a controlled project scope. Functional expectations
were centered on authentication, organization and class access, materials,
assignments, examinations, results, notifications, live sessions, AI support,
and programming-oriented learning support. At the same time, non-functional
considerations such as maintainability, usability, responsiveness, and secure
role separation were treated as necessary foundations rather than optional
additions.

Scope definition was especially important because Eduverse includes both web
and mobile clients. The main web platform was assigned responsibility for the
full academic environment, including management and richer interactive
workflows, whereas the mobile client was intentionally limited to MVP
companion responsibilities such as authentication, dashboard access, classes,
assignments, notifications, chat, materials, and live sessions. Advanced
mobile parity was deliberately excluded from the current development scope.

\subsection{System Design and Architecture Planning}\label{subsec:system_design_and_architecture_planning}

Once the scope was defined, the project moved into high-level system planning.
This phase established the platform as an integrated educational environment
with clearly separated responsibilities across the client interface, secure
server-side operations, structured data management, large-file handling,
real-time communication, and AI-assisted support. The intention was not to
over-engineer the system, but to create a structure capable of supporting
multiple educational workflows without losing coherence.

Architecture planning also involved deciding how different types of platform
data and services should be managed. Structured and frequently queried
institutional data were aligned with Supabase PostgreSQL, large academic files
were aligned with AWS S3, real-time live teaching sessions were aligned with
LiveKit, and AI assistance was aligned with an external model-access layer.
This planning phase created the conceptual foundation for the later
implementation decisions described in subsequent chapters.

\subsection{Web Application Development}\label{subsec:web_application_development}

The main body of development work was concentrated on the web application
because it serves as the primary environment for the complete Eduverse
platform. Development proceeded through feature-oriented iterations in which
shared educational workflows were implemented, reviewed, and refined in
relation to the user roles and class-centered structure identified earlier.

Within this phase, the web platform evolved to support the major academic
functions of the system, including organization and role handling, class
management, materials, assignments, examinations, results, notifications, live
sessions, AI interaction, and the educational IDE. Although these features are
discussed in more technical detail later, their methodological significance
here lies in the fact that they were not treated as isolated pages. They were
developed as connected parts of one integrated platform model.

\subsection{Mobile Companion Development}\label{subsec:mobile_companion_development}

The mobile application was developed as an MVP companion rather than as a full
replication of the web platform. This methodological decision preserved the
project's realism by recognizing that mobile interaction patterns differ from
desktop-oriented academic management workflows. The mobile effort therefore
focused on high-frequency participation tasks that are valuable in day-to-day
educational use.

In practical terms, the mobile scope emphasized authentication, dashboard
visibility, classes, assignments, notifications, chat, materials, and live
session participation. This kept the companion application aligned with the
main platform while avoiding unsupported claims of complete feature parity.
Administrative workflows, advanced authoring, broader analytics, and richer
management functions were intentionally left to the web platform or deferred as
future work.

\subsection{Backend, Database, and Service Integration}\label{subsec:backend_database_and_service_integration}

Another major phase concerned integrating the system components that allow the
platform to operate as one coherent environment. This included secure
authentication handling, API-based data exchange, role-aware access control,
database-backed academic workflows, large-file access, live-session support,
and AI service connectivity. Methodologically, this phase was important because
integration quality directly affected whether Eduverse behaved like a unified
platform or merely a group of adjacent features.

The project therefore adopted a service-aware integration strategy. Structured
academic records were maintained in Supabase PostgreSQL, large learning files
and submission-related assets were handled through AWS S3, real-time session
capabilities were connected through LiveKit, and AI support was connected
through OpenRouter. The mobile companion relied on the same identity and
backend ecosystem, which helped preserve consistency between the two clients
without duplicating platform ownership logic.

\subsection{Testing and Refinement}\label{subsec:testing_and_refinement}

The final recurring phase involved testing and refinement across the evolving
system. Verification was not limited to one late-stage activity; it accompanied
development through repeated checking of feature behavior, role restrictions,
integration points, and interface consistency. This was especially important
for workflows such as examinations, live sessions, and IDE-supported learning,
where reliability affects both user trust and academic credibility.

The refinement process combined targeted automated checks with iterative manual
review. Available tests and quality checks focused on selected core logic such
as examination behavior, IDE runners, feature selection logic, and related
supporting components, while manual review remained important for integrated
user flows across roles and devices. Full end-to-end automation was outside the
current project scope, so iterative correction and controlled verification were
used to stabilize the implemented platform.

\section{Tools and Technologies Used in the Development Process}\label{sec:tools_and_technologies_used}

The development process relied on a technology set selected to support a
modern, maintainable educational platform without fragmenting the project into
unrelated systems. The main implemented client was built as a web application
using Next.js, React, TypeScript, and Tailwind CSS. The companion mobile
application was built using Expo, React Native, and TypeScript in order to
support selected mobile workflows within the same broader platform direction.

For data and service integration, the project used Supabase for authentication
and structured platform data, AWS S3 for larger academic files, LiveKit for
real-time live sessions, and OpenRouter for AI Agent connectivity. These
technologies are identified here as part of the methodological environment of
the project; their detailed technical roles are discussed in later chapters.
Detailed technical analysis of each technology and its implementation role is
reserved for Chapter 6.

\section{Team Workflow and Project Management}\label{sec:team_workflow_and_project_management}

The project workflow emphasized continuous coordination between analysis,
implementation, and documentation. Rather than separating the work into fully
independent tracks, the team progressed through repeated cycles in which
requirements were clarified, features were prioritized, implementation choices
were reviewed against scope, and documentation was updated to reflect verified
project realities.

Priority was consistently given to the workflows that define Eduverse as an
integrated educational platform. This meant that class-centered activities,
role-sensitive access, assessment support, live sessions, and controlled mobile
extension received more attention than peripheral or purely decorative
features. Such prioritization helped the team preserve academic relevance and
avoid uncontrolled expansion beyond the graduation-project scope.

\section{Methodological Challenges}\label{sec:methodological_challenges}

One of the main methodological challenges in Eduverse was balancing feature
breadth with controlled scope. The platform combines educational management,
communication, assessment, real-time teaching, AI support, and programming
practice, all of which could easily lead to over-expansion. This challenge was
addressed by keeping the web platform as the main implementation target and by
treating the mobile client as an MVP companion with intentionally limited
responsibilities.

Another challenge concerned integration complexity. Multi-organization access,
role-aware behavior, live sessions, storage separation, and AI support all
required careful coordination so that the system would remain coherent rather
than fragmented internally. A further challenge was maintaining accurate
documentation boundaries, especially when distinguishing between features that
are already implemented and features that remain under development. These
constraints reinforced the importance of iterative refinement and disciplined
scope management throughout the project.

\section{Summary}\label{sec:methodology_summary}

This chapter has described the methodology through which Eduverse was planned,
developed, integrated, and refined as a graduation project. The project
followed an iterative, feature-oriented approach that supported gradual
validation of scope, roles, services, and user workflows. This methodological
foundation prepares the transition to the next chapter, which examines the
system analysis and requirement structure in greater detail.
