\chapterwithopening{Strategic Vision and Project Scope}{chap:strategic_vision}{
  \chaptercontentsitem{sec:general_introduction}
  \chaptercontentsitem{sec:problem_statement}
  \chaptercontentsitem{sec:project_motivations}
  \chaptercontentsitem{sec:strategic_objectives}
  \chaptercontentsitem{sec:team_goals}
  \chaptercontentsitem{sec:project_scope}
  \chaptercontentsitem{sec:report_organization}
}

\section{General Introduction}\label{sec:general_introduction}

Digital transformation has changed how educational institutions manage
teaching, communication, assessment, and academic follow-up. Despite this
shift, many institutions still rely on fragmented combinations of messaging
applications, file-sharing tools, video-conferencing platforms, and manually
coordinated assessment processes. Such fragmentation reduces continuity in the
learning experience, increases administrative overhead, and weakens the
institutional ability to manage educational workflows within one controlled
environment.

Eduverse is an integrated educational platform developed to address this
problem through a unified, multi-organization, role-based environment. Its
main implemented client is a web application, supported by an MVP mobile
companion application that extends access to selected academic workflows for
students and teachers. The platform is centered on the class as the primary
digital workspace in which materials, assignments, examinations, results,
notifications, live sessions, academic communication, and intelligent support
services can be managed in a coordinated manner.

At a high level, Eduverse combines a modern web platform with supporting cloud
and real-time services in order to provide a realistic and extensible
educational system. The web client is built using Next.js, React, TypeScript,
Tailwind CSS, and Supabase, while the mobile companion is built using Expo,
React Native, and TypeScript. These technologies are mentioned here only as an
introductory overview; detailed technical analysis and implementation
discussion are reserved for later chapters.

\section{Problem Statement}\label{sec:problem_statement}

Educational institutions often manage closely related academic tasks through
separate systems that are not designed to operate as one coherent platform.
Materials may be distributed through one service, communication may take place
in another, live teaching may depend on a third platform, and assessment
records may be maintained elsewhere. As a result, students are forced to move
between disconnected interfaces, while teachers and administrators struggle to
maintain consistent oversight of participation, submissions, communication, and
evaluation.

This problem becomes more serious in institutions that must manage multiple
organizations, classes, and user roles under different access conditions. A
practical educational platform must support not only learning activities, but
also institutional control, membership management, and role-based access across
different organizational contexts. Without these capabilities, digital
education systems tend either to become rigid and limited or to become too
loosely structured to support reliable academic administration.

A further challenge concerns platform coverage across devices. Rich authoring,
administration, and class management workflows are best handled through a full
web environment, whereas frequent day-to-day actions such as checking classes,
following notifications, viewing assignments, opening materials, joining live
sessions, and reading messages must also be accessible on mobile devices. This
creates a need for an educational platform centered on a comprehensive web
environment, supported by a practical mobile companion rather than a simplistic
one-client-for-all approach.

\section{Project Motivations}\label{sec:project_motivations}

The development of Eduverse is motivated by the need to provide a unified
academic environment in which essential educational workflows can be carried
out without fragmentation. A coherent class-centered system can improve the
student experience, reduce operational burden for teachers and administrators,
and strengthen institutional visibility over communication, assessment, and
academic progress.

The project is also motivated by the growing demand for flexible educational
infrastructure. Modern institutions often require platforms that can support
multiple organizations, distinct user roles, synchronous and asynchronous
learning activities, and selective feature enablement within one extensible
environment. Eduverse responds to this need by combining institutional control
with practical support for daily teaching and learning workflows.

From an academic perspective, Eduverse is also motivated by its value as a
software engineering project. It provides a realistic setting in which
requirements analysis, interface planning, system integration, data management,
real-time communication, AI-assisted services, and technical documentation can
be studied and implemented within one coherent graduation project context.

\section{Strategic Objectives}\label{sec:strategic_objectives}

At the strategic level, Eduverse aims to establish an integrated educational
platform whose primary implemented client is a web application, complemented by
an MVP mobile companion application, in order to centralize essential academic
workflows for organizations, teachers, and students within one role-aware and
extensible system.

The main strategic objectives of the project are as follows:

\begin{itemize}
  \item To centralize core educational workflows such as class management,
    materials, assignments, examinations, results, notifications,
    communication, and live sessions within one coordinated platform.
  \item To support multi-organization operation and role-based access for
    organization owners, organization admins, teachers, and students.
  \item To provide a primary web-based environment capable of supporting both
    institutional administration and day-to-day academic activity.
  \item To extend selected high-frequency academic workflows to a mobile MVP
    companion application without claiming full feature parity with the web
    platform.
  \item To incorporate distinctive educational capabilities such as an AI
    Agent and an integrated educational IDE as part of the platform's broader
    academic value.
  \item To organize data and services in a maintainable and scalable manner
    suitable for educational institutions with different operational needs.
  \item To produce a graduation project that is both academically meaningful
    and practically relevant as a modern educational software platform.
\end{itemize}

\section{Educational and Professional Goals for the Team}\label{sec:team_goals}

Eduverse also serves clear educational and professional goals for the project
team. From an educational standpoint, it provides an opportunity to apply
software engineering concepts to a realistic problem domain rather than to an
isolated classroom exercise. The team must analyze institutional needs, define
system boundaries, organize requirements, structure user roles, and translate
these decisions into a functional digital platform.

From a professional standpoint, the project strengthens practical experience in
requirements analysis, frontend development, backend integration, database
usage, real-time service integration, collaborative development workflows, and
technical documentation. It therefore contributes not only to the production of
software, but also to the development of disciplined engineering practice,
teamwork, and academic reporting skills.

\section{Project Scope and Boundaries}\label{sec:project_scope}

The scope of Eduverse in this dissertation is defined around the implemented web
platform and the existing mobile MVP companion application. Chapter 1 is
limited to introducing the problem context, strategic direction, main user
groups, system boundaries, and general dissertation structure. Detailed
requirements, architecture, database design, implementation decisions, and
testing evidence are reserved for later chapters.

\subsection{System Boundaries and User Roles}\label{subsec:system_boundaries_roles}

Eduverse operates within a multi-organization educational context and therefore
distinguishes clearly between administrative, instructional, and learner
responsibilities. At the institutional level, the platform supports
organization owners and organization admins who manage organizations, user
access, and operational control. At the instructional level, teachers manage
class activities such as materials, assignments, live sessions, examinations,
and academic follow-up. At the learner level, students access the classes to
which they belong in order to study materials, follow announcements, submit
work, join sessions, communicate, and review academic outcomes.

These role distinctions define important system boundaries. Eduverse is not a
generic social platform in which all users have the same functional position.
Instead, access is governed by organizational membership, class context, and
academic responsibility. This role-aware structure supports accountability,
controlled visibility, and more reliable institutional management.

\subsection{Functional Scope}\label{subsec:functional_scope}

Within its current implemented scope, Eduverse includes authentication,
multi-organization access, class management, materials, assignments, exams,
results, notifications, live sessions, an AI Agent, and an integrated
educational IDE. Together, these functions define the platform as more than a
basic learning content portal. Eduverse is intended to support both academic
management and active instructional workflows within one system.

At the same time, Chapter 1 remains introductory in nature. It does not attempt
to document detailed database structures, API behavior, or low-level internal
logic. Those aspects are part of the later analytical and technical chapters
and lie outside the present scope.

\subsection{Web and Mobile Client Scope}\label{subsec:web_mobile_client_scope}

The main implemented Eduverse client is the web application. It provides the
widest operational coverage of the platform, including organization-aware
navigation, role-based access, class management, materials, assignments, exams,
results, notifications, live sessions, AI Agent workflows, and the integrated
educational IDE. For this reason, the web application should be regarded as the
core working environment of the system.

The mobile application has a more focused scope. It is an MVP companion
application intended to extend access to selected academic workflows such as
authentication, dashboard viewing, classes, assignments, notifications, chat,
materials, and live sessions. Although it is connected to the same broader
platform environment, it is not yet feature-complete relative to the web
application and should therefore be described as a companion application rather
than a replacement for the primary platform.

\subsection{Competitive Features and Technological Innovation}\label{subsec:competitive_features_innovation}

Eduverse is distinguished by the combination of features it brings together in
one educational platform. A major distinguishing point is its
multi-organization, role-based structure, which allows the same system to
support organizational control, instructional management, and student
participation in a coordinated way. The platform also integrates live sessions,
an AI Agent, and an educational IDE within the same broader academic
environment rather than treating them as isolated external utilities.

Another important feature is the platform's attention to examinations and
assessment integrity. Eduverse does not treat evaluation as a peripheral task,
but as an integral part of the educational workflow that must be managed within
a controlled digital environment. In addition, the system deliberately combines
a comprehensive web platform with an MVP mobile companion application, thereby
balancing rich institutional workflows with accessible everyday mobile use.

From a technological perspective, Eduverse also reflects a deliberate service
separation strategy. Structured and frequently queried academic data are stored
through Supabase PostgreSQL, large educational files are handled through AWS
S3, and real-time live-session interaction is supported through LiveKit. This
separated storage and service model strengthens the platform's practicality for
an educational environment that must manage both relational records and larger
real-time or file-based workloads.

\section{Report Organization}\label{sec:report_organization}

This dissertation is organized as follows. Chapter 2 presents the literature
review and theoretical framework. Chapter 3 describes the adopted methodology.
Chapter 4 covers system analysis and requirements. Chapter 5 presents system
design. Chapter 6 discusses software and engineering implementation.
Chapter 7 presents testing and evaluation. Chapter 8 addresses future work and
planned extensions, followed by the conclusion and appendices.
